Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Revised intro

Data available from the interaction is also used to increase the engegment of 
users in the system by applying  gamification techniques. Gamification is defined by 
Deterding et al. \cite{deterding2011game} as
\begin{quote}
  the use of game design elements in non-game contexts.
\end{quote}  
The gamification element employed in this case study has been a rewarding mechanism  
\cite{dubois2013understanding}. In general rewards  consist of a reputation system 
with score points, levels and leader boards. Points are awarded to users in response of 
the accomplishment of certain activities that need to be encouraged. Levels depend
on the score and certain features of the game are only available to gamers when 
they reach a giving level. % Say what we are doing in this case - JJ
%%%
%%% Change if case studies change
%In this work, a case study consisting in a web application for evolving artistic drawings
%is presented, providing both conceptual and implementation details of the framework. 
%In order to test the framework three versions of the application are compared to
%measure the degree of relationship between users and their participation,
%when appling a gamification technique. 
In this work, three case studies are presented. First, the development of a web based C-IEC application 
for evolving artistic drawings is described to give the reader details about 
the utilization of the proposed framework. Then, a rewarding mechanism is 
implemented in the same application to study the changes in participation
when applying a gamification technique. Finally, two other case studies are briefly presented
to show how the framework is applied to other domains.

The rest of this paper is organized as follows.
Section \ref{sec:related} presents related work on the topic 
of interactive evolution. Then, Section \ref{sec:framework} presents the human centered framework of
for C-IEC appliactions which the main proposal of this work. The implementation of the data model
is detailed in Section \ref{sec:implementation}. Next three case studies are presented: EvoDrawings in
Section \ref{sec:evodraw}, EvoDraw Installation in Section\ref{sec:evodraw}, 
and XYZ in Section\ref{sec:evodraw}. Finally, a concluding remarks are provided 
in Section \ref{sec:conclusions}.

>>>>

Data available from the interaction is also used to increase the engegment of 
users in the system by applying  gamification techniques. Gamification
is a technique defined by 
Deterding et al. \cite{deterding2011game} as
\begin{quote}
  the use of game design elements in non-game contexts.
\end{quote}  
The gamification element employed in this case study has been a rewarding mechanism  
\cite{dubois2013understanding}. In general rewards  consist of a reputation system 
with score points, levels and leader boards. Points are awarded to users in response of 
the accomplishment of certain activities that need to be encouraged. Levels depend
on the score and certain features of the game are only available to gamers when 
they reach a giving level. % Say what we are doing in this case - JJ
%%%
%%% Change if case studies change
%In this work, a case study consisting in a web application for evolving artistic drawings
%is presented, providing both conceptual and implementation details of the framework. 
%In order to test the framework three versions of the application are compared to
%measure the degree of relationship between users and their participation,
%when appling a gamification technique. 
In this work, three case studies are presented. First, the development of a web based C-IEC application 
for evolving artistic drawings is described to give the reader details about 
the utilization of the proposed framework. Then, a rewarding mechanism is 
implemented in the same application to study the changes in participation
when applying a gamification technique. Finally, two other case studies are briefly presented
to show how the framework can applied to other domains. %The
                                %objectives of these lasts are... - JJ

The rest of this paper is organized as follows.
Section \ref{sec:related} presents related work on the topic 
of interactive evolution. Then, Section \ref{sec:framework} presents the human centered framework of
for C-IEC appliactions which the main proposal of this work. The implementation of the data model
is detailed in Section \ref{sec:implementation}. % Why not all case
                                % studies in the same section? - JJ
Next three case studies are presented: EvoDrawings in
Section \ref{sec:evodraw}, EvoDraw Installation in Section\ref{sec:evodraw}, 
and XYZ in Section\ref{sec:evodraw}. Finally, concluding remarks are provided 
in Section \ref{sec:conclusions}.
